---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# dualchain

The goal of dualchain is to help create good and bad MCMC samples for an upcoming experiment

## Installation

You can install dualchain from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("njtierney/dualchain")
```

## Example

This is mainly for Miles:

Create the samples
```{r run-samples}
library(dualchain)
lawful_good <- mcmc_generator(max_mixtures = 2,
                              burn_in = 100,
                              samples = 100,
                              extra_sample = 1000)

chaotic_evil <- mcmc_generator(max_mixtures = 10,
                               burn_in = 100,
                               samples = 100,
                               extra_sample = 1000)

```

Create the raw lineup data
```{r raw-data}

raw_data <- prepare_raw_lineup(good_mcmc_list = lawful_good$extra_eyes,
                               evil_mcmc_list = chaotic_evil$extra_eyes,
                               n_chain = 1)
raw_data

```

Create the lineup data
```{r create-lineup}

data_lineup <- add_groups_and_facets(raw_data)

data_lineup

```

create the solution

```{r create-solution}

lineup_solution <- retrieve_lineup_solution(data_lineup)
lineup_solution
```

Create the plots

The regular `gg_` plots return a plot invisibly

```{r show-plots}
ac <- gg_mcmc_autocor(data_lineup)
den <- gg_mcmc_density(data_lineup)
tra <- gg_mcmc_trace(data_lineup)

ac
den
tra
```

You can also call them directly like so:
```{r mcmc-diagnostic-plot}
mcmc_diagnostic_plot(data_lineup, plot_type = "trace")
```

And here is the list to pass to shiny

```{r generate-experiment}
clos <- generate_experiment(good_mcmc = lawful_good$extra_eyes,
                            bad_mcmc = chaotic_evil$extra_eyes,
                            n_chain = 1,
                            plot_type = "trace")

clos()

```

